Using SMT engine to generate Symbolic Automata\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2017-06-23 2017-Xudong-SMT/submit-ICTAC2017.tex
Improve the Algorithm 1.

\State Initialize sets $U$, $E$ for unexplored/explored global states
$U$, $L$ for result OTs;
\While{!isEmpty(U)}
	\State Chose a global state $S$ in $U$; recursively applying Tr1 or Tr2 on the root node;
	\If{Subnet is a pLTS}
                \State $s$ is the local state of the pLTS in the global state $S$;
		\For{each transition $tr$ starting from $s$}
			\State apply Tr1 to build the corresponding
                        $OT$; store $OT$ in $L$; \EndFor
	\EndIf
	\If{Subnet is a pNet, apply Tr2:} 
		\For{each $sv \in SV$}
			\State Invoke $Combining()$ to generate the
                        combination of sub-transitions, $Matching()$
                        to match the combination with the $sv$; then
                        store the result OTs in    $L$; 
		\EndFor
	\EndIf
	\For{each target global state $T$ from $OT \in L$}
		\IfThen{$(!U.contains(T))\ \&\&\ (!E.contains(T))$}{Add $T$ into the $U$;}
	\EndFor
\EndWhile
\State Prune the open transitions in $L$ using the SMT solver;
\State \Return $L$;

>>>>

\State Initialize sets $U$, $E$ for unexplored/explored global states
$U$, $L$ for result OTs;
\While{!isEmpty(U)}
	\State Chose a global state $S$ in $U$; recursively applying Tr1 or Tr2 on the root node;
	\If{Subnet is a pLTS}
                \State Get the local state of the pLTS $s$ from $S$;
		\For{each transition $tr$ starting from $s$} Apply Tr1
			\State Build the corresponding
                        $OT$; store $OT$ in $L$; 
                 \EndFor
	\EndIf
	\If{Subnet is a pNet}
		\For{each $sv \in SV$} Apply Tr2
			\State Invoke $Combining()$ to generate the
                        combination of sub-transitions, $Matching()$
                        to match the combination with the $sv$; Store the result OTs in $L$; 
		\EndFor
	\EndIf
	\For{each target global state $T$ from $OT \in L$}
		\IfThen{$(!U.contains(T))\ \&\&\ (!E.contains(T))$}{Add $T$ into the $U$;}
	\EndFor
\EndWhile
\State Prune the open transitions in $L$ using the SMT solver;
\State \Return $L$;
